Alexis Roche

### 2021-03-05 cv/cv.tex
update cv

\noindent Scientific team leader with a specialist expertise in computer vision, data science and machine learning, who has operated in the fields of academic research, healthcare, electro-domestic and entertainment industry. Graduated from \'Ecole Centrale Paris, and holder of a PhD in Engineering Science. Strong experience in the development of both open source and commercial software. {\em Keywords:} artificial intelligence, image processing, computer vision, medical image analysis, machine learning, deep learning, statistics, Python,~C.

@@

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Publications:}
\ \\ 
\ \\
\ \\
\ \\
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} 115 scholarly publications.\\
{\tiny$\bullet$} Full list available at ORCID: \url{http://orcid.org/0000-0002-4821-6893} \\
{\tiny$\bullet$} Google scholar statistics: 6225 citations, h-index: 32, i10-index: 63 (December 2020).\\
{\tiny$\bullet$} 5 published international patents. \\
\end{minipage}

>>>>

\noindent Hands-on scientific team leader, graduated from \'Ecole Centrale Paris, PhD, with a specialist expertise in computer vision, data science and machine learning. Has operated in the fields of academic research, healthcare, electro-domestic and entertainment industry. Strong experience in the development of both open source and commercial software. {\em Keywords:} artificial intelligence, image processing, computer vision, medical image analysis, machine learning, deep learning, statistics, Python,~C.

@@

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Publications:}
\ \\ 
\ \\
\ \\
\ \\
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} 115 scholarly publications.\\
{\tiny$\bullet$} Full list available at ORCID: \url{http://orcid.org/0000-0002-4821-6893} \\
{\tiny$\bullet$} Google scholar statistics: 6322 citations, h-index: 32, i10-index: 65 (March 2021).\\
{\tiny$\bullet$} 5 published international patents. \\
\end{minipage}
